\documentclass[MTech]{iitddiss}
% \settopmatter{printacmref=false}

\input{macros}
\usepackage{t1enc}

\usepackage{graphicx}
\usepackage{hyperref} % hyperlinks for references.
\usepackage{amsmath} % easier math formulae, align, subequations \ldots
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{natbib}
\usepackage{fancyhdr}
 \linespread{1.2}

\pagestyle{fancy}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}

\fancyhf{}

\rhead{\fancyplain{}{\thepage}} % predefined ()
\lhead{\fancyplain{}{\rightmark}} % 1. sectionname, 1.1 subsection name etc
\cfoot{\textcopyright \text{ } \the\year, \emph{Indian Institute of Technology Delhi}}
\renewcommand{\footrulewidth}{0.4pt}
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title page

\title{An Approximate Algorithm for Mining Top-$k$ Correlated Subgraphs in a Large Graph}

\author{Arneish Prateek}
\advisor{Prof. Sayan Ranu}
\entrynumber{2014CH10786}
\date{June 2019}
\department{Computer Science and Engineering}

%\nocite{*}
\maketitle


% \pagenumbering{arabic}

% \copyrightyear{2020}
% \acmYear{2020}
% \setcopyright{acmcopyright}
% \acmConference[SIGMOD '20]{ACM SIGMOD '20: ACM International Conference on Management of Data}{June 14--19, 2020}{Portland, Oregon, USA}
% \acmPrice{15.00}
% \acmDOI{10.1145/1122445.1122456}
% \acmISBN{978-1-4503-9999-9/18/06}

% \begin{document}

% \title{}

% \author{}
% \advisor{Sayan Ranu}
% \department{Computer Science and Engineering}

%\author{Arijit Khan} \affiliation{\institution{Nanyang Technological
%University}
%}
%\email{arijit.khan@ntu.edu.sg}
%
%\author{Arneish Prateek} \affiliation{\institution{Indian Institute of
%Technology Delhi, India}
%}
%\email{ch1140786@iitd.ac.in}
%
%\author{Sayan Ranu} \affiliation{\institution{Indian Institute of Technology
%Delhi, India}
%}
%\email{sayanranu@iitd.ac.in}
%
%\author{Akshit Goyal} \affiliation{\institution{Indian Institute of Technology
%Delhi, India}
%}
%\email{cs5140278@iitd.ac.in}

% \maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Certificate
\certificate

\vspace*{0.5in}

\noindent This is to certify that the thesis titled {\bf\ An Approximate
Algorithm for Mining Top-$k$ Correlated Subgraphs in a Large Graph} submitted
by {\bf Arneish Prateek}, to Indian Institute of Technology, Delhi, for
the award of the degree of {\bf Master of Technology}, is a bonafide
record of the research work done by him under our supervision.  The
contents of this thesis, in full or in parts, have not been submitted
to any other Institute or University for the award of any degree or
diploma.

\vspace*{1.5in}

\begin{singlespacing}
\hspace*{-0.25in}
\parbox{2.5in}{
\noindent {\bf Prof.~1} \\
\noindent Professor Sayan Ranu\\
\noindent Dept of CSE\\
\noindent IIT-Delhi, 110016 \\
}
\hspace*{1.0in}
\end{singlespacing}
\vspace*{0.25in}
\noindent \hfill Place: New Delhi\\
\noindent \hfill Date: June 25, 2019\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Acknowledgements

\acknowledgements

This thesis is the outcome of a joint collaborative effort with \textbf{Akshit Goyal}
(Master's Candidate, IIT Delhi). The author of this thesis has attempted to
demarcate the contributions of the collaborator and himself to the best of his
abilities. For a complete guide to this project, this thesis must be read in
conjunction with the thesis titled \textbf{An Exact Algorithm for Mining Top-$k$
Correlated Subgraphs in a Large Graph} by \textbf{Akshit Goyal}. Appendix I contains
the complementary sections from this other thesis. The following chapters are
common to both theses:

\textbf{Chapter 1}

\textbf{Chapter 2}

\textbf{Chapter 3}: Sections 3.1,3.2,3.3,3.4

\textbf{Chapter 4}: Section 4.1



\begin{abstract}
	Mining of correlated patterns, that represent an important class of
	regularities, has become increasingly important in data management and
	analytics. Surprisingly, the problem of correlated subgraphs mining from a
	single, large graph has received little attention. We investigate a novel and
	critical graph mining problem, called {\em correlated subgraphs mining} ({\sf{CSM}}), 
	which is defined as a pair of subgraph patterns that frequently co-occur in proximity
	within a single graph.
	
	Correlated subgraphs are different from frequent subgraphs due to the
	flexibility in which the constituent subgraph instances are connected, thus the
	existing frequent subgraphs mining algorithms cannot be directly applied.
	Furthermore, correlation computation between two subgraph patterns require
	enumerating and finding distances between every pair of subgraph instances of
	both these patterns --- which is memory intensive and computationally
	demanding.
	
	To this end, we design two novel, holistic, best-first exploration algorithms: {\sf{CSM-E}}
	(an exact method) and {\sf{CSM-A}} (a more efficient, approximate method with near-optimal
	quality). To further improve their efficiency, we propose a top-$k$ pruning strategy, 
	while to reduce memory footprints, we develop a compressed data structure, 
	$\mathcal{R}$eplica, that stores all instances of a subgraph pattern on demand. 
	Our empirical results show that the proposed algorithms not only find interesting correlations, 
	but also achieve good scalability over large networks.
	\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table of contents etc.

\begin{singlespace}
\tableofcontents
\thispagestyle{empty}

% \listoftables
% \addcontentsline{toc}{chapter}{LIST OF TABLES}
% \listoffigures
% \addcontentsline{toc}{chapter}{LIST OF FIGURES}
\end{singlespace}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abbreviations
% \abbreviations

% \noindent
% \begin{tabbing}
% xxxxxxxxxxx \= xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
% \textbf{IITD}   \> Indian Institute of Technology, Delhi \\
% \textbf{RTFM} \> Read the Fine Manual \\
% \end{tabbing}

% \pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Notation

% \chapter*{\centerline{NOTATION}}
% \addcontentsline{toc}{chapter}{NOTATION}

% \begin{singlespace}
% \begin{tabbing}
% xxxxxxxxxxx \= xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
% \textbf{$r$}  \> Radius, $m$ \\
% \textbf{$\alpha$}  \> Angle of thesis in degrees \\
% \textbf{$\beta$}   \> Flight path in degrees \\
% \end{tabbing}
% \end{singlespace}

% \pagebreak
% \clearpage

% The main text will follow from this point so set the page numbering
% to arabic from here on.
\pagenumbering{arabic}

\vspace{-4mm}




\input{introduction}
\input{preliminaries}
\input{exact_algo_new}
\input{approx_algo}

% \input{overview} \input{searchTree} \input{calculation}
% \input{algorithm}
% \input{correlatedGroup}

\input{experiments}
\input{related}
\input{conclusions}

\appendix

\chapter{The Exact Algorithm for Correlated Subgraph Mining}

The following algorithm is reported verbatim from the thesis titled 
\textbf{An Exact Algorithm for Mining Top-$k$ Correlated Subgraphs in a Large
Graph} by \textbf{Akshit Goyal}. For a detailed analysis of the exact
strategy, the reader can refer to Akshit Goyal's thesis. 

% stored in $DFS\ List$.
\begin{algorithm}
  \dontprintsemicolon
  \nonl \TitleOfAlgo{\textsc{A.1: FindAllInstancesExact()} }\;
  % \caption{\textsc{FindAllInstances} \textsc{(Exact)}}\label{algo:complete-instances}
	\nonl \textbf{Input:} Graph $G$, parent $Q$, $replica(Q)$, child $R$, $DFS$ $List$, partial isomorphism of $R$: $instance$, $\mathbb{I}$\;
	% parent edge: $(u, v)\in E(G)$ mapped to $(u',v')\in E(R)$,
	% \KwOut{$replica(R)$}
	\nonl \textbf{Output:} $\mathbb{I}: $ set of all instances of $R$ in $G$ consistent with input partial isomorphism $instance$\;
	%such that $\forall I \in \mathbb{I} $  $ (u',u),(v',v) \in I$)\;
	% \REQUIRE input graph: $G$, parent pattern: $Q$, replica of $Q$: $replica(Q)$, parent edge: $(u, v)$, $DFS\ List$ of $Q$ rooted at $extending\ index$, child pattern: $R$
	% \ENSURE all mappings of pattern $R$ in $G$ that include $(u, v)$
	\uIf{$|instance|=|V(R)|$}
	{
		\Return{$instance$}
	}
	\Else
	{
		$e(p,c) \coloneq$ \textsc{NextQueryEdge($DFS\ List, ...$)}\;
		$P_{c} \coloneq$ \textsc{FilterCandidates($instance, c, ...$)}\;
		\ForEach{$w \in P_{c}$ \textup{such that w is not yet matched}}
		{
			$instance \leftarrow instance \cup \{(c,w)\}$\;
			$\mathbb{I} \leftarrow \mathbb{I}\ \cup$ \textsc{FindAllInstances($R,instance,$ ...)}\;
			$instance \leftarrow instance \setminus \{(c,w)\}$\;
		}
		\Return{$\mathbb{I}$}\;
	}
	% \IF{all $edges$ in $DFS\ List$ have been mapped}
	% \STATE \textbf{return} $instance$ set
	% \ENDIF
	% \FORALL{adjacent edges $e$ of $v$ in $replica(Q)$}
	% \IF{$e$ maps to the corresponding $child\ edge$ in $DFS\ List$ \textbf{and} \textbf{not} already in $instance$}
	% \STATE $instance\leftarrow instance\cup e$
	% \STATE $\mathbb{I}\leftarrow \mathbb{I}\ \cup\ ${\sf find\ all\ instances($R$, $e$, $instance$, $DFS\ List$)}
	% \STATE $instance\leftarrow instance \setminus e$
	% \ENDIF
	% \ENDFOR
	% \STATE \textbf{return} $\mathbb{I}$
\end{algorithm}


\begin{algorithm}%[h!]
  \nonl \TitleOfAlgo{\textsc{A.2: OperateExact()} }\;
  % \begin{algorithmic}[1]
		\dontprintsemicolon
		\nonl \textbf{Input:} Graph $G$, $Q$, $replica(Q)$, hop $h$, $CorV$, $CorP$\;
		\nonl \textbf{Output:} $\tau({Q,Q_{k},h})$, updated {\sf Top\ $k$} order\;
		% $DFS\ List\leftarrow$ get rooted {\sf DFS} of $Q$ with $center$ as $root$\;
		% \ForEach{\textup{mapping $m$ of $center$ in $replica(Q)$}}
		\ForEach{\textup{vertex $m \in Mappings(center, replica(Q))$}}
		{
      $\mathbb{I}\leftarrow$ {set of all instances $I$ such that $(center, m)\in I$}\;
      \nonl [[Found Using \textsc{FindAllInstancesExact}]] \;
			\ForEach{$u\in V(replica(Q))$ \textup{constituing an $instance$ in} $\mathbb{I}$}
			{
				$\forall v \in CorV(u)$, $CorP(v)\leftarrow CorP(v) \cup \{Q\}$\;
				$Collect(m, Q) \leftarrow Collect(m, Q) \cup CorP(u)$\;	 
			}						
		}
		\ForEach{\textup{pattern $Q_k$ in set {\sf operated}}}
		{
			% $\tau(Q, Q_k, h)\leftarrow$ number of instance group centers $m$ s.t. $Q_k\in Collect(m, Q)$\;
			$\tau(Q, Q_k, h)\leftarrow$  $|\{m$ | $m\in Mappings(center,$ $replica(Q)$) $\wedge$ $Q_k\in Collect(m, Q)\}|$\;
		}
		Update {\sf Top\ $k$} order with computed correlation ($\tau$) values\;
		{\sf operated} $\leftarrow$ {\sf operated} $\cup \ \{Q\}$\;
\end{algorithm}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{-2mm}
{\scriptsize
\bibliographystyle{abbrv} %\enlargethispage*{3\baselineskip}
\bibliography{ref}
}


\end{document}


